%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\newsectionwidth{0pt} % Stops section indenting

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{Thomas Veale\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

% \address{{\bf School Address} \\ Department of Study \\ University \\ City, State 12345 \\ (000) 111-1111} % Your address 1

% \address{{\bf Permanent Address} \\ 123 Broadway \\ City, State 12345 \\ (000) 111-1111} % Your address 2

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{OBJECTIVE}}

\vspace{8pt} % Gap between title and text

Hands on tehcnica lead with strong track record at startups. Global experience working in cross functional teams to increase velocity and deliver valie. Interests lean towards rapid prototyping, automation, and telemetry. Open to new positions within R&D, product, or technical.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EDUCATION}} 

\vspace{8pt} % Gap between title and text

{\sl PhD Computer Science, (incomplete)}, 
Cyrpography, Cryptosystems\\ 
Virginia Commonwealth University, Richmond, VA \hfill Dec 2017\\ 
THESIS - Novel consensus algorithms, e.g. proof of stake \\
 
{\sl Bachelor of Science}, Computer Science\\ 
Virginia Commonwealth University, Richmond, VA \hfill Dec 2015\\ 
Focus in cyber security

%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PROFESSIONAL EXPERIENCE}} 

\vspace{8pt} % Gap between title and text

{\sl Bullish Global, Hong Kong} \hfill Dec 2021 --  \\
SRE \hfill 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Brought new crypto exchange into operation by supporing the operational staff with tactical software to monitor trading system health.
\item Merge telemetry into single unitifed search on Datadog. Moving several thousand instances, enforcing reasonable cost model for users, instrumented apps, developed tagging strategies and educational resources.
\item Run effective monitoring strategy and deliver key business intelligence to leadership.
\item Modernized observability practices by implemented distributed tracing, re-working metrics, introducing structured logging, and building black-box montoring system for SLO/SLI.
\item Support product launches with production readiness reviews to ensure smooth launch of key products market-making, margin, dated futures, perpetuals, options, volatility, and FIX. 
\item Develop and maintain effective relationships with various teams to maximize customer satisfcation.
\item Utilize frequent automated testing to simuate disaster scenarios and accurately idenitfy and measure ability to respond problems.
\item Simplfy operations with automatic syncronization between the various observability, incident, change, and problem managment systems. Streamlined tooling reduces cognative load.
\item Statsd, Datadog, Otel, Gitops, Python, Java, GCP, AWS, Azure, OVH, Digital Ocean.
\end{itemize}

{\sl Finverse Technology, Hong Kong} \\[2pt]
Developer \hfill June 2020 -- November 2021 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item First hire at Asia open banking data-aggregation outfit
\item Push multi-functional team to adapt and refine gitops best practices. Upfront cost of streamling and automating builds/deploys payed off quickly.
\item Ran cycle planning and ceremonies, tracked metrics, improved process. Interviewed, mentored, and  trained junior devs.
\item Greenfield project to production SaaS product with dozens of bank connections in 6mo. Infra and frameworks we wrote still run today.
\item Core tech: Goloang, postgres, gcp, python, nodejs, puppeteer
\item Event Sourcing, CQRS, Reverse Engineering, API/Test drive development
\end{itemize} 

\vspace{-6pt} % Reduce space between positions at the same organization
Neat (A Rapyd company, Hong Kong)\hfill September 2019 -- Feb 2020 \\
Developer
\begin{itemize} 
\item Improve product release times by strangling standalone services out of monoloth. Removed 10s of thousands of lines of code from maintenance and build times by a minute.
\item Harden user account security with account takeover prevention software that locks accounts based on risk and behavior.
\item Reduce friction with onboarding new customers thru a simple, automated signup application that meets compliance needs.
\item Prootype tool that parses new user applications using NLP/ML and web queries to produce a risk score that automates some manual tasks by compliance officers and reduced the load on compliance team eliminating many false positives.
\end{itemize}
 
{\sl Makecents, New York, NY} \hfill July 2016 -- August 2019 \\
Developer
\begin{itemize}
\item Hire and run mixed team of 10+ to build mobile payments system in 6 months.
\item Deploy and support procuct for large interstate retailer. 
\item Negotate terms for compute cost share and subscription model for revanue.
\item Business development activites, public speaking, investor talks. Raise US \$0.5mm
\end{itemize}

{\sl Graduare Research Assistent} \hfill Aug 2015 -- December 2016 \\ Richmond, VA
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Implement stochastic experiments to simulate performance of consensus algorithms in distributed systems.
\item Mentored and trained undergraduates students.
\item Developed research, technical writing, and peer reviews.
\item Ran community study group for cryptograpy, bitcoin, and blockchain.
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{COMPUTER SKILLS}}

\vspace{8pt} % Gap between title and text

Professional with golang, typescript, javascript, java, rust, python, git.\\
Configure and operate kafka, kubernetes, open telemetry, argocd, various cloud platforms.\\
Infra as code, observability as code. Familar with C/C++, Clojure, Ocaml, Erlang, others.\\
%Familiar with many languages including C/C++, Pascal, Fortran, Clojure, Cobol, Scala, Akka, Ocaml, Erlang\\
Leader in running SDLC. Comfortable in scrub, kanban, scrumban, gitops, or other agile practices.\\
Proficient in remote access, network managment, system adminstration\\
Acedemic training in maths, statstics, algorithms, modern cryptography, distributed systems.\\
Working knowledge of superviced machine learning, transformers, neaural networks, computer vision, and natural language processing,\\
Frameworks includer Flask, Vue, Angulaar, Django, Micronaut, Airflow, Flux, Rails, Sinatra, swagger.\\
Comfortable with decompilers, payload injectors, fuzzers, scanners among other secuirty tooling.\\
%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

%\section{\centerline{PUBLICATIONS}} 

%\vspace{15pt} % Gap between title and text
%\\begin{itemize} \itemsep -2pt % Reduce space between items
%\item ``Job Analysis - A True Picture," Journal of Headhunters, Vol. 5, Number 3. Fall 1990 
%\item ``The Fine Tuning of Interpersonal Skills," Journal of Recruiting/Hiring, Vol. 16, Number 7, August 1990
%\end{itemize}

%----------------------------------------------------------------------------------------

% \vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------

%\section{\centerline{MEMBERSHIPS}} 

%\vspace{-5pt} % Reduce space between section title and contents

%\begin{center}
%\end{center}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	HONORS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{HONORS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Bitcoin School Greece (2016) - EU Intel Grant\\
BitCamp Hackathon (2016) - RedHat Open source Award\\
\end{center}

%----------------------------------------------------------------------------------------

%\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{INTERESTS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Ultimate, trail running, bouldering, cooking, music, sci-fi, open source
\end{center} 

%----------------------------------------------------------------------------------------

\end{resume} 
\end{document}